Understanding Implications of Dataset Choice for Feature Effect Estimation: A Simulation-Based Investigation through Error Decomposition

### 2025-02-08 paper/paper.tex
paper: add main experiment result plots and refine bibliography

\documentclass[runningheads]{llncs}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{booktabs} 
\usepackage{svg}
\usepackage[misc]{ifsym}
\newcommand{\corr}{(\Letter)}
% N.B.: do not change anything above this line. If you require additional packages, please load them directly after this line.
\usepackage{mwe}
% N.B.: you may delete the preceding line. It is used to display an example image in this template.

@@

>>>>

\documentclass[runningheads]{llncs}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{booktabs} 
\usepackage{subcaption}
\usepackage[misc]{ifsym}
\newcommand{\corr}{(\Letter)}
% N.B.: do not change anything above this line. If you require additional packages, please load them directly after this line.
\usepackage{mwe}
% N.B.: you may delete the preceding line. It is used to display an example image in this template.

@@

\subsection{Main Experiment}

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{img/SNC/feature_effect_errors_pdp_GAM_OF.png}
        \caption{GAM\_OF}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{img/SNC/feature_effect_errors_pdp_GAM_OT.png}
        \caption{GAM\_OT}
    \end{subfigure}
    \\[10pt]
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{img/SNC/feature_effect_errors_pdp_XGBoost_OF.png}
        \caption{XGBoost\_OF}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{img/SNC/feature_effect_errors_pdp_XGBoost_OT.png}
        \caption{XGBoost\_OT}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{img/SNC/feature_effect_errors_pdp_SVM_OT.png}
        \caption{SVM\_OT}
    \end{subfigure}
    \caption{Main experiment results for PDP on SimpleNormalCorrelated dataset. \dots}
    \label{fig:pdp-results-snc}
 \end{figure}

 \begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{img/SNC/feature_effect_errors_ale_GAM_OF.png}
        \caption{GAM\_OF}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{img/SNC/feature_effect_errors_ale_GAM_OT.png}
        \caption{GAM\_OT}
    \end{subfigure}
    \\[10pt]
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{img/SNC/feature_effect_errors_ale_XGBoost_OF.png}
        \caption{XGBoost\_OF}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{img/SNC/feature_effect_errors_ale_XGBoost_OT.png}
        \caption{XGBoost\_OT}
    \end{subfigure}
    \\[10pt]
    \vfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{img/SNC/feature_effect_errors_ale_SVM_OT.png}
        \caption{SVM\_OT}
    \end{subfigure}
    \caption{Main experiment results for ALE on SimpleNormalCorrelated dataset. \dots}
    \label{fig:ale-results-snc}
 \end{figure}
